\plaintitle

### 2018-02-14 paper_deutsch/main.tex
Titel angepasst
Ergebnisse Bild um 90 grad gedreht. Bilder Zentriert. Pfade angeasst. Diskussionsergebnisse in die Abgabe eingefügt
löschen des Copyrights, Anpassen des Ausblicks

% Copyright
\CopyrightYear{2018}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
% ISBN
%Conference
%Price

@@

%% HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP --
%% Please note you need to make sure the copy for your specific
%% license is used here!
% \toappear{
% Permission to make digital or hard copies of all or part of this work
% for personal or classroom use is granted without fee provided that
% copies are not made or distributed for profit or commercial advantage
% and that copies bear this notice and the full citation on the first
% page. Copyrights for components of this work owned by others than ACM
% must be honored. Abstracting with credit is permitted. To copy
% otherwise, or republish, to post on servers or to redistribute to
% lists, requires prior specific permission and/or a fee. Request
% permissions from \href{mailto:Permissions@acm.org}{Permissions@acm.org}. \\
% \emph{CHI '16},  May 07--12, 2016, San Jose, CA, USA \\
% ACM xxx-x-xxxx-xxxx-x/xx/xx\ldots \$15.00 \\
% DOI: \url{http://dx.doi.org/xx.xxxx/xxxxxxx.xxxxxxx}
% }

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Parallel World}
\def\plainauthor{Dimitrie Diez, Daniel Graf, Ludwig Wagner}
\def\emptyauthor{}
\def\plainkeywords{Authentifizierung; Authentifizierungsmechanismus; Authentifizierungskonzept; Fake-Profil; Parallel World; Always Login; Fake-Welt; Soziales Netzwerk; Sicherheitskonzept}

@@

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  pdfdisplaydoctitle=true, % For Accessibility
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

@@

\category{K.6.5}{Management of Computing and Information Systems}{Security and Protection} 
\category{K.4.2}{Computers and Society}{Social Issues}
\todo[inline]{Abklären in der Gruppe ob nicht mehr Ergebnisse ins abstract müssen, klare Aussage, dass Fokus auf USABILITY liegt}
\keywords{\plainkeywords}

@@

	\includegraphics[width=0.8\columnwidth]{figures/LoginVorgang.PNG}

@@

@@

\todo[inline]{Offene Punkte: Probleme bei der Umsetzung beschreiben (Limitierende Faktoren), Bewertung des Konzept im Paper(z.B Dieses Verfahren macht alle geklauten Daten nutzlos, da nicht sicher ob sie korrekt sind), Ausarbeitung welche Teilkonzepte am erfolgversprechendsten sind, welche sind nicht machbar}

@@

\clearpage
\onecolumn
\section{Anhang}
\begin{figure*}[h]
	\centering
	\includegraphics[width=\columnwidth]{figures/Social-Networks.png}
	\caption{Ergebnisse der Fokusgruppe und der Einzelbefragung}
	\label{fig:MindMapAnhang}
\end{figure*}
\newpage
\begin{figure*}[h]
	\centering
	\includegraphics[width=0.8\columnwidth]{figures/Fragebogen.pdf}
	\caption{Aufbau des Fragebogens für die Einzelbefragungen}
	\label{fig:Fragebogen}
\end{figure*}

>>>>

% Copyright
%\CopyrightYear{2018}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
% ISBN
%Conference
%Price

@@

%% HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP --
%% Please note you need to make sure the copy for your specific
%% license is used here!
\toappear{2018 Hochschule München}

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Secure Social Network - Parallel World}
\def\plainauthor{Dimitrie Diez, Daniel Graf, Ludwig Wagner}
\def\emptyauthor{Dimitrie Diez, Daniel Graf, Ludwig Wagner}
\def\plainkeywords{Authentifizierung; Authentifizierungsmechanismus; Authentifizierungskonzept; Fake-Profil; Parallel World; Always Login; Fake-Welt; Soziales Netzwerk; Sicherheitskonzept}

@@

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfdisplaydoctitle=true, % For Accessibility
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

@@

%\category{K.6.5}{Management of Computing and Information Systems}{Security and Protection} 
%\category{K.4.2}{Computers and Society}{Social Issues}
\todo[inline]{Abklären in der Gruppe ob nicht mehr Ergebnisse ins abstract müssen, klare Aussage, dass Fokus auf USABILITY liegt}
%\keywords{\plainkeywords}

@@

\centering
	\includegraphics[width=0.8\columnwidth]{figures/Loginvorgang.png}

@@

\centering

@@

Ein solcher Prototyp kann Probleme bei der Umsetzung aufzeigen und limitierende Faktoren definieren. Darüber hinaus kann dadurch bewertet werden, welche Teilkonzepte am erfolgversprechendsten und welche nicht machbar sind.

@@

\clearpage
\onecolumn
\section{Anhang}
\begin{figure}[h]
	\centering
	\includegraphics[height=0.76\textheight]{figures/Social-Networks.png}
	\caption{Ergebnisse der Fokusgruppe und der Einzelbefragung}
	\label{fig:MindMapAnhang}
\end{figure}
\newpage
\begin{figure*}[h]
	\centering
	\includegraphics[width=0.8\columnwidth]{figures/Fragebogen.pdf}
	\caption{Aufbau des Fragebogens für die Einzelbefragungen}
	\label{fig:Fragebogen}
\end{figure*}
